---
title: "p8105_hw1_yme2112"
output: github_document
---

Loading necessary data set from "moderndive" package

```{r} 
library(moderndive)
data("early_january_weather")

```

## Let's take a look at the data 

```{r}
View(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```


This data shows the weather data for EWR airport in January of 2013 with 15 
variables found in `ncol(early_january_weather)` and 358 entries from 
`nrow(early_january_weather)`. Important variables `time_hour`(date and hour)
,`temp`(temperature in F), `precip` (precipitation in inches), help determine 
environmental conditions in the hour. The mean temperature is 39.58F as said 
in `mean(early_january_weather$temp)`.

## Let's make a scatter plot and save it

```{r}
library(ggplot2)

january_plot = ggplot(data = early_january_weather,
       aes(x = time_hour, y = temp, color = humid)) +
  geom_point()

ggsave("january_scatterplot.png", plot = january_plot)

```


From what we can see, after January 10th there were more instances of humidity.
Most of the humid days occurred when the temp was between 40 and 50F.





