---
title: "p8105_hw1_yme2112"
output: github_document
---

Loading necessary data set from "moderndive" package

```{r setup, message= FALSE} 
library(moderndive)
data("early_january_weather")
library(ggplot2)
library(tidyverse)
```

## Let's take a look at the data 

```{r}
View(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```


This data shows the weather data for EWR airport in January of 2013 with 15 
variables found in `ncol(early_january_weather)` and 358 entries from 
`nrow(early_january_weather)`. Important variables `time_hour`(date and hour)
,`temp`(temperature in F), `precip` (precipitation in inches), help determine 
environmental conditions in the hour. The mean temperature is 39.58F as said 
in `mean(early_january_weather$temp)`.

## Let's make a scatter plot and save it

```{r}
january_plot = ggplot(data = early_january_weather,
       aes(x = time_hour, y = temp, color = humid)) +
  geom_point()

ggsave("january_scatterplot.png", plot = january_plot)

```


From what we can see, after January 10th there were more instances of humidity.
Most of the humid days occurred when the temp was between 40 and 50F.

## Let's do Problem 2

```{r}
problem_df =
  tibble(
    vec_numeric = rnorm(10),
    vec_logic = vec_numeric > 0, 
    vec_length = sample(c("red","yellow","blue"), size = 10, replace = TRUE),
    vec_factor = factor(sample(c("low", "medium", "high"), size = 10, replace = TRUE))
  )
```

now, lets find the mean and try out our new pipe function we learned!

```{r}
mean(problem_df|> pull(vec_numeric))
mean(pull(problem_df,vec_logic))
mean(problem_df |> pull(vec_length))
mean(problem_df |> pull(vec_factor))
```

The last two vectors labled as `vec_factor` and `vec_length` are not numerically
based, but character based and that's why there is no mean.

```{r}
num_logic = as.numeric(problem_df |> pull(vec_logic))
num_length = as.numeric(problem_df |> pull(vec_length))
num_factor = as.numeric(problem_df |> pull(vec_factor))
```

`num_length` comes up as an error. Character means cannot be found because it 
is text. However, the `num_factor` came up as an error in mean but not 
`as.numeric` which is because in the background, R transforms these factor
labels into numbers that represent them.


